A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-05-13 none_feedback_sequence_classifier/doc/main.tex

@@

In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
at every 10 {\it ms}, which is the usual frame period in speech 
recognition
\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
Using three two-to-one max-pool layers, $\vec{z}[p]$ has a frame period 
of 80 {\it ms}.  
The relationship between the temporal index $p$ in $\vec{z}[p]$ and 
$m$ in $\vec{x}[m]$ is given by: 
\begin{align}
  p = \lceil m / 8 \rceil \label{eq:def_p}
\end{align}
\begin{align}
  \mathcal{Z}_{0}^{M-1}  =  
    \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
  \label{eq:frame_target_label}
\end{align}

@@

The first step is making an
alignment using the N-best alignment. The second step is updating the
neural network parameters using the Cross Entropy (CE) criterion.

@@

The first step is finding the optimal frame-synchronous sequence
$\mathcal{Z}_0^{M-1}$.

>>>>

 In Fig. 
\ref{fig:ctc_diagram} $\sim$ \ref{fig:attention_diagram}, we show
block diagrams of CTC \cite{a_graves_icml_2006_00}, 
RNN-T \cite{a_graves_corr_2012_00, a_graves_icassp_2013_00}, and 
the attention-based model 
\cite{
j_chorowski_nips_2015_00,
w_chan_icassp_2016_00} respectively. CTC in Fig. \ref{fig:ctc_diagram} 
and RNN-T in Fig. \ref{fig:rnn_t_diagram} are {\it frame-synchronous}, 
which means that the ASR system generates the output target for each 
input frame.

@@

In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
at every 10 {\it ms}, which is the usual frame period in speech 
recognition
at every 10 {\it ms}, which is the usual speech feature frame rate  
in speech recognition
\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
Using three two-to-one max-pool layers, $\vec{z}[p]$ has a frame period 
of 80 {\it ms}.  
The relationship between the temporal index $p$ in $\vec{z}[p]$ and 
$m$ in $\vec{x}[m]$ is given by: 
\begin{align}
  p = \lceil m / 8 \rceil \label{eq:def_p}
\end{align}
\begin{align}
  \mathcal{Z}_{0}^{M-1}  =  
    \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
  \label{eq:frame_target_label}
\end{align}

@@

The first step is making an
In this section, we describe how to train FSC. The first step is making an
>>>>>>> cf67f8b3ff96936469f82b1916daebe02799ed40
alignment using the N-best alignment. The second step is updating the
neural network parameters using the Cross Entropy (CE) criterion.

@@

The first step is finding the optimal frame-synchronous sequence
$\mathcal{Z}_0^{M-1}$.   
$\mathcal{Z}$
